Open archaeology, open source?

### 2024-07-13 analysis/_06-network.qmd
Add R2 values to plots
As suggested by JW

```{r fig-repo-betweenness-age-length}
#| fig-cap: Repository centrality by age (left) and length (right). Centrality is measured by node betweenness weighted by number of contributions. Blue line indicates a generalized linear regression, with confidence envelope shaded in grey.
left <- oarch_graph_repo_repo |>
  as_tibble() |> 
  left_join(oarch, by = c("repo" = "gh_repo")) |>
  mutate(
    age = map_int(gh_commits, \(x) min(today() - date(x$datetime)))
  ) |>
  ggplot(aes(age, betweenness)) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10(labels = NULL) +
  geom_smooth(method = "glm") +
  labs(x = "Days", y = "Log centrality →") +
  theme_oarch()

right <- oarch_graph_repo_repo |>
  as_tibble() |> 
  left_join(oarch, by = c("repo" = "gh_repo")) |>
  mutate(
    length = map_int(gh_commits, nrow)
  ) |>
  ggplot(aes(length, betweenness)) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10(labels = NULL) +
  geom_smooth(method = "glm") +
  labs(x = "Commits", y = NULL) +
  theme_oarch()

@@

```{r fig-user-betweenness-contribs}
#| fig-cap: User centrality by total number of contributions. Centrality is measured by node betweenness weighted by number of contributions.  Blue line indicates a generalized linear regression, with confidence envelope shaded in grey.
oarch_graph_user_user |>
  as_tibble() |> 
  left_join(oarch_contributors, by = c("user" = "contributor")) |>
  ggplot(aes(contribs, betweenness)) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10() +
  geom_smooth(method = "glm") +
  labs(x = "Total contributions", y = "Centrality") +
  theme_oarch()
```

>>>>

```{r fig-repo-betweenness-age-length}
#| fig-cap: Repository centrality by age (left) and length (right). Centrality is measured by node betweenness weighted by number of contributions. Blue line indicates a generalized linear regression, with confidence envelope shaded in grey.
left <- oarch_graph_repo_repo |>
  as_tibble() |> 
  left_join(oarch, by = c("repo" = "gh_repo")) |>
  mutate(
    age = map_int(gh_commits, \(x) min(today() - date(x$datetime)))
  ) |>
  ggplot(aes(age, betweenness)) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10(labels = NULL) +
  geom_smooth(method = "lm") +
  stat_poly_eq(method = "lm") +
  labs(x = "Days", y = "Log centrality →") +
  theme_oarch()

right <- oarch_graph_repo_repo |>
  as_tibble() |> 
  left_join(oarch, by = c("repo" = "gh_repo")) |>
  mutate(
    length = map_int(gh_commits, nrow)
  ) |>
  ggplot(aes(length, betweenness)) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10(labels = NULL) +
  geom_smooth(method = "lm") +
  stat_poly_eq(method = "lm") +
  labs(x = "Commits", y = NULL) +
  theme_oarch()

@@

```{r fig-user-betweenness-contribs}
#| fig-cap: User centrality by total number of contributions. Centrality is measured by node betweenness weighted by number of contributions.  Blue line indicates a generalized linear regression, with confidence envelope shaded in grey.
oarch_graph_user_user |>
  as_tibble() |> 
  left_join(oarch_contributors, by = c("user" = "contributor")) |>
  ggplot(aes(contribs, betweenness)) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10() +
  geom_smooth(method = "lm") +
  stat_poly_eq(method = "lm") +
  labs(x = "Total contributions", y = "Centrality") +
  theme_oarch()
```

### 2024-07-13 analysis/openarchaeo_collaboration.qmd
Add R2 values to plots
As suggested by JW

```{r dependencies}
library("english")
library("fs")
library("ggiraph")
library("ggraph")
library("glue")
library("here")
library("khroma")
library("lubridate")
library("patchwork")
library("rgexf")
library("scales")
library("tidygraph")
library("tidyverse")
library("tinytable")
```

>>>>

```{r dependencies}
library("english")
library("fs")
library("ggiraph")
library("ggraph")
library("ggpmisc")
library("glue")
library("here")
library("khroma")
library("lubridate")
library("patchwork")
library("rgexf")
library("scales")
library("tidygraph")
library("tidyverse")
library("tinytable")
```
